### 2015-07-13 thesis/thesis/chap3/chap3.tex
changes

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=2.8in]{Figures/task_done_opt.eps}
\includegraphics[width=2.8in]{Figures/task_qos_opt.eps}
\caption{Part (a): Cumulative number of requests successfully
done. Part (b): Average QoS of requests performed.}
\label{performanceall}
\end{figure}

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{Figures/least_core.eps}
\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
\end{figure}

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{Figures/s2_task_done.eps}
\includegraphics[width=3in]{Figures/s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks succesfully done. Part
(b): Average QoS of tasks performed.} \label{performancemany}
\end{figure}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{Figures/taxtation.eps}
\caption{Analysis of community subsiding coefficient $\lambda$ on
average community size (a), cost (b), number of tasks performed
(c), and average quality of service of tasks performed (d).}
\label{f_taxtation}
\end{figure*}

@@

\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the community coordinator would be interested in paying
web services in order to keep the group reliable from the end
user's point of view.
\centerline{\includegraphics[width=6.8in]{Figures/tax_dyn.eps}}
\caption{Analysis of community subsiding coefficient $\lambda$
having web service different stability levels of $\tau$ on average
community size, number of tasks performed, average quality of
service, and average cost/income of communities.}
\label{fig_dynamic_taxtation}
\end{figure*}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=2.5in]{Figures/s2_task_done.eps}
\includegraphics[width=2.5in]{Figures/s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks successfully done.
Part (b): Average QoS of tasks performed.} \label{performancemany}
\end{figure*}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=1.9in]{Figures/avg_task_ws_done.eps}
\includegraphics[width=1.9in]{Figures/avg_qos_ws_done.eps}
\includegraphics[width=1.9in]{Figures/avg_avail_ws_done.eps}
\caption{A comparison between our community model and the High
Availability Coalition model from \cite{10.1109/TSC.2012.12}. Part
(a): Cumulative number of tasks successfully done. Part (b):
Average QoS of tasks performed. Part (c): Average community
service availability} \label{fig_avail_method}
\end{figure*}

>>>>

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3.5in]{Figures/task_done_opt.eps}
\includegraphics[width=3.5in]{Figures/task_qos_opt.eps}
\caption{Part (a): Cumulative number of requests successfully
done. Part (b): Average QoS of requests performed.}
\label{performanceall}
\end{figure}

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3.5in]{Figures/least_core.eps}
\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
\end{figure}

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3.5in]{Figures/s2_task_done.eps}
\includegraphics[width=3.5in]{Figures/s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks succesfully done. Part
(b): Average QoS of tasks performed.} \label{performancemany}
\end{figure}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=4in]{Figures/taxtation.eps}
\caption{Analysis of community subsiding coefficient $\lambda$ on
average community size (a), cost (b), number of tasks performed
(c), and average quality of service of tasks performed (d).}
\label{f_taxtation}
\end{figure*}

@@

\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the community coordinator would be interested in paying
web services in order to keep the group reliable from the end
user's point of view.
\centerline{\includegraphics[width=7in]{Figures/tax_dyn.eps}}
\caption{Analysis of community subsiding coefficient $\lambda$
having web service different stability levels of $\tau$ on average
community size, number of tasks performed, average quality of
service, and average cost/income of communities.}
\label{fig_dynamic_taxtation}
\end{figure*}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3.5in]{Figures/s2_task_done.eps}
\includegraphics[width=3.5in]{Figures/s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks successfully done.
Part (b): Average QoS of tasks performed.} \label{performancemany}
\end{figure*}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3.5in]{Figures/avg_task_ws_done.eps}
\includegraphics[width=3.5in]{Figures/avg_qos_ws_done.eps}
\includegraphics[width=3.5in]{Figures/avg_avail_ws_done.eps}
\caption{A comparison between our community model and the High
Availability Coalition model from \cite{10.1109/TSC.2012.12}. Part
(a): Cumulative number of tasks successfully done. Part (b):
Average QoS of tasks performed. Part (c): Average community
service availability} \label{fig_avail_method}
\end{figure*}

### 2015-07-13 thesis/thesis/chap6/chap6.tex
changes

In this theses we proposed three models for aggregation of web services within communities. The goal of our models are to maximize efficiency by collaborating and forming stable communities. In our first contributions we focused on stability and fairness for all web services within the communities. This model offers an applicable mechanism for membership requests and selection of serb services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality.

In our next step of research work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behaviour of intelligent services that are active within communities. We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this paper are also backed by simulation results using a real services dataset. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits. Thus, deviating from our coopetitive strategy yields less income for the service.

In our final step of the work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and  membership management in communities of web services. This mechanism helps web services and communities decide with whom to be grouped and cooperate. DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain. In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility. The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature. The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

>>>>

In this theses we proposed three models for aggregation of web services within communities. The goal of our models are to maximize efficiency by collaborating and forming stable communities. In our first contributions we focused on stability and fairness for all web services within the communities. In this work we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and also fairness and stability of communities. The proposed model offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality.

In our next step of research work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and membership management in communities of web services. In this work we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services. The proposed mechanism helps web services and communities decide with whom to be grouped and cooperate. DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain. In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility. The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature. The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our final step of the work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behaviour of intelligent services that are active within communities. We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this thesis are also backed by simulation results using a real services dataset. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits. Thus, deviating from our coopetitive strategy yields less income for the service.

%Our plan for future work is to advance learning process on the training set that we provided in our work. SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

%As future work in this area, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.

%As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally. Moreover, we would like to achieve a collusion resistant efficiency mechanism, which is still an open problem in open environments.
